---
title: "HW1-My Data Science Profile"
author: "Nanmanat Disayakamonpan"
format: 
  html: 
    code-fold: true
editor: source
---

```{r load-packages-and-data, message = FALSE}
#| echo: false
# Load packages and data
library(tidyverse)
profiles <- read_csv("data/ourdatascienceprofiles.csv")
```

## My data science profile

```{r my-data-science-profile}
#| echo: false
myname <- "Nanmanat Disayakamonpan"
profiles |> 
  pivot_longer(`Social Science`:`Machine Learning`, names_to = "Dimension") |> 
  filter(Name == myname) |> 
  ggplot(aes(x = value, y = Dimension)) + 
  geom_col(fill = "darkred") +
  labs(title = myname)
```

As you can see the graph for my data science profile, it is noticeable that **the business** is my strongest dimension with the value of 10. On the other hand, my weakest dimensions are **programming and machine learning** with the value of 1.

## Out data science group

```{r mean-dimension-values}
#| echo: false
profiles |> 
  summarize(across(`Social Science`:`Machine Learning`, mean))
```

The dimension with the most experience in the group is **Data Visualization** with ***a value of 6.85***.

The dimension with the least experience in the group is **Machine Learning** with ***a value of 2.85***.

## Operating Systems in our group

```{r operating-systems}
#| echo: false
profiles |> 
  group_by(`What is the operating system of your computer?`) |> 
  count()
```

## Use of Artificial Intelligence in our group

```{r use-of-artificial-intelligence-1}
#| echo: false
profiles |> 
  ggplot(data =profiles, mapping =aes(x =`Have you used AI Tools (like GitHub Copilot) while writing code?`)) +
  geom_bar(fill = "blue") 
```

```{r use-of-artificial-intelligence-2}
#| echo: false
profiles |> 
  ggplot(data =profiles, mapping =aes(x =`Have you used AI Tools (like ChatGPT) to draft text for you?`)) +
  geom_bar(fill = "red")
```

```{r use-of-artificial-intelligence-3}
#| echo: false
profiles |>
  ggplot(data =profiles, mapping =aes(x =`Have you chatted with AI Tools (like ChatGPT) to learn about a new topic?`)) +
  geom_bar(fill = "yellow")
```
